### 2017-01-17 text/Chapter05.tex
Edits pages 31-94

The semantics of variable access and abstraction are the same as in the semantics of Uustalu and
Vene \cite{comonads-notions}, modulo the indexing. The semantics of variable access (\emph{var}) uses
$\ident{counit}_{\cunit}$ to extract a product of free variables, followed by projection
$\pi_i$ to obtain the variable value. Abstraction (\emph{abs}) is interpreted as a curried
function that takes the declaration-site context and a function argument, merges them using
$\ident{merge}_{\cclrd{r}, \cclrd{s}}$ and passes the result to the semantics of the body $f$.
Assuming the context $\Gamma$ contains variables of types $\sigma_1, \ldots, \sigma_n$, this gives
us a value $\ctyp{\cclrd{r}\czip\cclrd{s}}((\sigma_1 \times \ldots \times \sigma_n) \times \tau_1)$.
Assuming that $n$-element tuples are associated to the left, the wrapped context is equivalent to
$\sigma_1 \times \ldots \times \sigma_n \times \tau_1$, which can then be passed to the body of the
function.

@@

For the semantics of implicit parameter programs that we consider, the preference of call site
bindings over declaration-site bindings in (\emph{merge}) does not matter. The unique typing
derivations for implicit parameter coeffects obtained in Section~\ref{sec:flat-unique} always
split implicit parameters into \emph{disjoint sets}, so preferences do not come into play.

>>>>

The semantics of variable access and abstraction are the same as in the semantics of Uustalu and
Vene \cite{comonads-notions}, modulo the indexing. The semantics of variable access (\emph{var}) uses
$\ident{counit}_{\cunit}$ to extract a product of free variables, followed by projection
$\pi_i$ to obtain the variable value. Abstraction (\emph{abs}) is interpreted as a curried
function that takes the declaration site context and a function argument, merges them using
$\ident{merge}_{\cclrd{r}, \cclrd{s}}$ and passes the result to the semantics of the body $f$.
Assuming the context $\Gamma$ contains variables of types $\sigma_1, \ldots, \sigma_n$, this gives
us a value $\ctyp{\cclrd{r}\czip\cclrd{s}}((\sigma_1 \times \ldots \times \sigma_n) \times \tau_1)$.
Assuming that $n$-element tuples are associated to the left, the wrapped context is equivalent to
$\sigma_1 \times \ldots \times \sigma_n \times \tau_1$, which can then be passed to the body of the
function.

@@

For the semantics of implicit parameter programs that we consider, the preference of call site
bindings over declaration site bindings in (\emph{merge}) does not matter. The unique typing
derivations for implicit parameter coeffects obtained in Section~\ref{sec:flat-unique} always
split implicit parameters into \emph{disjoint sets}, so preferences do not come into play.
